Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-10-19 ms.Rnw
Minor changes

mod3_n_params <- 10 * length(unit_specific_names) + length(shared_param_names)

@@

  N_SEARCHES <- 2L
} else if (RUN_LEVEL == 2) {
  SEARCH1 = list(
    NBPF = 20,
    NP = 500,
    SPAT_REGRESSION = 0.05,
    NREPS = 36,
    NP_EVAL = 1000,
    NREPS_EVAL = 12,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

  SEARCH2 = list(
    TOP_N = 6,
    NBPF = 20,
    NP = 500,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 1000,
    NREPS_EVAL = 12,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

  SEARCH3 = list(
    TOP_N = 6,
    NBPF = 20,
    NP = 500,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 1000,
    NREPS_EVAL = 12,
    RW_SD = chol_rw_3.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

@@

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/haiti3_coupled_fit.rds")) {
  haiti3_fit <- readRDS("model3/run_level_3/haiti3_coupled_fit.rds")
} else {
  haiti3_fit <- bake(
    file = paste0("model3/", rl_dir, "haiti3_coupled_fit.rds"), {
      fit_coupled_haiti3(
        nsearches = N_SEARCHES,
        search1 = SEARCH1,
        search2 = SEARCH2,
        search3 = SEARCH3,
        ncores = cores,
        search_rho = TRUE,
        search_gamma = TRUE
      )
    }
  )
}

@@

<<Table 2 Input, echo=FALSE, eval=TRUE>>=

NREPS_EVAL <- switch(RUN_LEVEL,   3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL, 100, 500,  5000)

@@

# h3Spat <- haiti3_spatPomp()
# coef(h3Spat) <- haitipkg:::panelParms_toSpatParms3(p3)

>>>>

mod3_n_params <- length(unit_specific_names) * 10 + length(shared_param_names)

@@

  N_SEARCHES <- 2L
} else if (RUN_LEVEL == 2) {
  SEARCH1 = list(
    NBPF = 25,
    NP = 500,
    SPAT_REGRESSION = 0.05,
    NREPS = 36,
    NP_EVAL = 1000,
    NREPS_EVAL = 12,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )

  SEARCH2 = list(
    TOP_N = 6,
    NBPF = 25,
    NP = 500,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 1000,
    NREPS_EVAL = 12,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )

  SEARCH3 = list(
    TOP_N = 6,
    NBPF = 25,
    NP = 500,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 1000,
    NREPS_EVAL = 12,
    RW_SD = chol_rw_3.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )

@@

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/haiti3_coupled_fit.rds")) {
  haiti3_fit <- readRDS("model3/run_level_3/haiti3_coupled_fit.rds")
} else {
  haiti3_fit <- bake(
    file = paste0("model3/", rl_dir, "haiti3_coupled_fit.rds"), {
      fit_coupled_haiti3(
        nsearches = N_SEARCHES,
        search1 = SEARCH1,
        search2 = SEARCH2,
        search3 = SEARCH3,
        ncores = cores,
        search_rho = TRUE,
        search_gamma = TRUE,
        search_Binit = FALSE
      )
    }
  )
}

@@

<<Table 2 Input, echo=FALSE, eval=TRUE>>=
NREPS_EVAL <- switch(RUN_LEVEL,   3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL, 100, 500,  5000)

@@
